---
title: "Handling FASTA sequences"
output:
  html_document: default
  html_notebook: default
---


#Load sequences using `read.table`: 


```{r}
fasta <- read.table("../deer_collagen_20170915.fasta", stringsAsFactors = F)
```

This gives us a simple table, the even rows of which are the sequences (in this particular application)


#Generating peptide sets

To construct the predicted peptides, you just call the function `parse.seq` and pass in the sequence data (even rows of the `fasta` object from above): 

```{r, echo=TRUE, message=FALSE}
#source("parse_seq.R")
require(bacollite, quietly = T) 

pep_elk <- parse.seq(fasta[2,])
pep_elk <- pep_elk[order(pep_elk$mass1),]

pep_deer <- parse.seq(fasta[4,])
pep_deer <- pep_deer[order(pep_deer$mass1),]



pep_elk_chymo <- parse.seq(fasta[2,],cuts="Y|F|W")
pep_elk_chymo <- pep_elk_chymo[order(pep_elk_chymo$mass1),]

pep_deer_chymo <- parse.seq(fasta[4,],cuts="Y|F|W")
pep_deer_chymo <- pep_deer_chymo[order(pep_deer_chymo$mass1),]

```

Note that to predict the peptides that come from treatment with chymotrypsin we've set the `cuts` variable to a regulare expression that lists the amino acids where chymotrypsin cuts. We'll look at the chymotrypsin peptides later on in this notebook.



#Processing the trypsin peptides



We can look at the elk peptides like this

```{r}
require(DT, quietly = T)
datatable(pep_elk)

```

you can sort this table by mass (the default), or by any other variable by clicking the triangles next to the column name. Note `seqpos` means the position in the sequence of the start of the peptide. Note that elk only seems to show two peptides with chymotrypsin

We can save these peptides to a csv file like this:

```{r}
write.csv(file="peptides_elk_trypsin.csv", pep_elk)
```



Here's and the deer: 

```{r}
datatable(pep_deer)
```

We can save these peptides to a csv file like this:

```{r}
write.csv(file="peptides_deer_trypsin.csv", pep_deer)
```


OK, we are now in a position to see which peptides match the spectra. 
We need a variable to hold the path to the files for the spectra.
We also need the fragment of each file path that refers to the replicate number:

```{r}
file_path <- "~/tmp/bioarch_kristine/spectra-trypsin/"
replicates <- c("_1","_2","_3")
```

##Processing elk samples: 

Now we need a list of the elk lots, which we will use to 'build' the file path for each replicate


```{r}
elk_lots <- c("P220a_elk",
              "P220b_elk",
              "P220c_elk",
              "P220d_elk",
              "P221a_elk",
              "P221b_elk",
              "P221c_elk",
              "P221d_elk"
)
```


We can generate the 'hits' between the peptides and the MALDI like this, with the output going to the file `elk.pdf`: 

```{r}
elk_hits<-list()
elk_data<-list()
pdf(file="elk.pdf",w=12,h=8)
for(ii in 1:length(elk_lots)){
  #message(sprintf("Opening %s%s%s.txt",file_path,elk_lots[ii],replicates[1]))
  froot <- sprintf("%s%s",file_path,elk_lots[ii])
  elk_data[[ii]] <- load.sample(froot=froot,name=sprintf("%s",elk_lots[ii]),replicates, fext = ".txt")
  elk_hits[[ii]] <- ms_fit(pep_elk,elk_data[[ii]],doplot=T,force=F)
}
dev.off()
```


A per-spectrum graphical summary of the matches can be created and placed in the file `elk_peaks.pdf` like so: 



```{r}
pdf(file="elk_peaks.pdf",w=24,h=8)
for(ii in 1:length(elk_lots)){
  
  data <- elk_data[[ii]]
  
  plot (x=data$s1$mass, y = data$s1$intensity/max(data$s1$intensity),type="l",col="red")
  lines(x=data$s2$mass, y = data$s2$intensity/max(data$s2$intensity), col = "green")
  lines(x=data$s3$mass, y = data$s3$intensity/max(data$s3$intensity), col = "blue")
  
  bzzt <- elk_hits[[ii]]
  bzzt <- cbind(bzzt,pep_elk)
  bzzt <- bzzt[bzzt$hit,]
  message(sprintf("drawing %d hits",nrow(bzzt)))
  points(x=bzzt$mass1,y=0.5*bzzt$mass1/bzzt$mass1,pch=20,cex=1.5,col="orange")
  
}
dev.off()
```


##processing red deer samples

The same process applies to deer - we just need to list the deer file bits like this:

```{r}
deer_lots <- c(
    "X4787a_reddeer",
    "X4787b_reddeer",
    "X4787c_reddeer",
    "X4787d_reddeer",
    "X4997a_reddeer",
    "X4997b_reddeer",
    "X4997c_reddeer",
    "X4997d_reddeer"
  )
```




OK, now we can go through the data and see which peptides fit which peaks, putting the output in `deer.pdf`: 

```{r}
deer_hits<-list()
deer_data<-list()
pdf(file="deer.pdf",w=12,h=8)
for(ii in 1:length(deer_lots)){
  #message(sprintf("Opening %s%s%s.txt",file_path,deer_lots[ii],replicates[1]))
  froot <- sprintf("%s%s",file_path,deer_lots[ii])
  deer_data[[ii]] <- load.sample(froot=froot,name=sprintf("%s",deer_lots[ii]),replicates, fext = ".txt")
  deer_hits[[ii]] <- ms_fit(pep_deer,deer_data[[ii]],doplot=T,force=F)
}
dev.off()
```

...and again make the per-spectrum summary file `deer_peaks.pdf`:

```{r}
pdf(file="deer_peaks.pdf",w=24,h=8)
for(ii in 1:length(elk_lots)){
  
  data <- deer_data[[ii]]
  
  plot (x=data$s1$mass, y = data$s1$intensity/max(data$s1$intensity),type="l",col="red")
  lines(x=data$s2$mass, y = data$s2$intensity/max(data$s2$intensity), col = "green")
  lines(x=data$s3$mass, y = data$s3$intensity/max(data$s3$intensity), col = "blue")
  
  bzzt <- deer_hits[[ii]]
  bzzt <- cbind(bzzt,pep_deer)
  bzzt <- bzzt[bzzt$hit,]
  message(sprintf("drawing %d hits",nrow(bzzt)))
  points(x=bzzt$mass1,y=0.5*bzzt$mass1/bzzt$mass1,pch=20,cex=1.5,col="orange")
  
}
dev.off()
```

##Cross-checking: elk spectra against deer sequence

Because the elk sequence is incomplete, it makes sense to see if any deer peptides explain the elk peaks


```{r}
elks_deerp_hits<-list()
pdf(file="elk_spec_vs_deer_peptides.pdf",w=12,h=8)
for(ii in 1:length(elk_lots)){
  elks_deerp_hits[[ii]] <- ms_fit(pep_deer,elk_data[[ii]],doplot=T,force=F)
}
dev.off()
```
...and again make the per-spectrum summary file `elk_spec_vs_deer_peptides_peaks.pdf`:

```{r}
pdf(file="elk_spec_vs_deer_peptides_peaks.pdf",w=24,h=8)
for(ii in 1:length(elk_lots)){
  
  data <- elk_data[[ii]]
  
  plot (x=data$s1$mass, y = data$s1$intensity/max(data$s1$intensity),type="l",col="red")
  lines(x=data$s2$mass, y = data$s2$intensity/max(data$s2$intensity), col = "green")
  lines(x=data$s3$mass, y = data$s3$intensity/max(data$s3$intensity), col = "blue")
  
  bzzt <- elks_deerp_hits[[ii]]
  bzzt <- cbind(bzzt,pep_deer)
  bzzt <- bzzt[bzzt$hit,]
  message(sprintf("drawing %d hits",nrow(bzzt)))
  points(x=bzzt$mass1,y=0.5*bzzt$mass1/bzzt$mass1,pch=20,cex=1.5,col="orange")
  
}
dev.off()
```

#Processing the chymotrypsin peptides

Let's look at the peptides for these first. Here's elk cut with chymotrypsin, and exported to a csv:

```{r}
datatable(pep_elk_chymo)
write.csv(file="peptides_elk_chymo.csv", pep_elk_chymo)
```

s and the deer: 

```{r}
datatable(pep_deer_chymo)
write.csv(file="peptides_deer_chymo.csv", pep_deer_chymo)
```

##Processing elk samples: 


Now we need a list of the elk lots, which we will use to 'build' the file path for each replicate


```{r}
elk_lots_chymo <- c("P220bc_elk",
              "P221bc_elk"
)
```

We need a variable to hold the path to the files.
We also need the fragment of each file path that refers to the replicate number:

```{r}
file_path_chymo <- "~/tmp/bioarch_kristine/spectra-chymotrypsin/"
```

OK, now we can go through the data and see which peptides fit which peaks: 

```{r}
elk_hits_chymo<-list()
elk_data_chymo<-list()
pdf(file="elk_chymo.pdf",w=12,h=8)
for(ii in 1:length(elk_lots_chymo)){
  #message(sprintf("Opening %s%s%s.txt",file_path_chymo,elk_lots_chymo[ii],replicates[1]))
  froot <- sprintf("%s%s",file_path_chymo,elk_lots_chymo[ii])
  elk_data_chymo[[ii]] <- load.sample(froot=froot,name=sprintf("%s",elk_lots_chymo[ii]),replicates, fext = ".txt")
  elk_hits_chymo[[ii]] <- ms_fit(pep_elk_chymo,elk_data_chymo[[ii]],doplot=T,force=F)
}
dev.off()
```
let's see what the elk per-spectra plots look like: 

```{r}
pdf(file="elk_peaks_chymo.pdf",w=24,h=8)
for(ii in 1:length(elk_lots_chymo)){

  data <- elk_data_chymo[[ii]]
  
  plot (x=data$s1$mass, y = data$s1$intensity/max(data$s1$intensity),type="l",col="red")
  lines(x=data$s2$mass, y = data$s2$intensity/max(data$s2$intensity), col = "green")
  lines(x=data$s3$mass, y = data$s3$intensity/max(data$s3$intensity), col = "blue")
  
  bzzt <- elk_hits_chymo[[ii]]
  bzzt <- cbind(bzzt,pep_elk_chymo)
  bzzt <- bzzt[bzzt$hit,]
  message(sprintf("drawing %d hits",nrow(bzzt)))
  points(x=bzzt$mass1,y=0.5*bzzt$mass1/bzzt$mass1,pch=20,cex=1.5,col="orange")
  
  
}
dev.off()
```




#Processing red deer samples





```{r}
deer_lots_chymo <- c(
    "X4787ac_reddeer",
    "X4997ac_reddeer"
  )
```




OK, now we can go through the data and see which peptides fit which peaks: 

```{r}
deer_hits_chymo<-list()
deer_data_chymo<-list()
pdf(file="deer_chymo.pdf",w=12,h=8)
for(ii in 1:length(deer_lots_chymo)){
  #message(sprintf("Opening %s%s%s.txt",file_path_chymo,deer_lots_chymo[ii],replicates[1]))
  froot <- sprintf("%s%s",file_path_chymo,deer_lots_chymo[ii])
  deer_data_chymo[[ii]] <- load.sample(froot=froot,name=sprintf("%s",deer_lots_chymo[ii]),replicates, fext = ".txt")
  deer_hits_chymo[[ii]] <- ms_fit(pep_deer_chymo,deer_data_chymo[[ii]],doplot=T,force=T)
}
dev.off()
```
let's see what the elk per-spectra plots look like: 

```{r}
pdf(file="deer_peaks_chymo.pdf",w=24,h=8)
for(ii in 1:length(deer_lots_chymo)){

  data <- deer_data_chymo[[ii]]
  
  plot (x=data$s1$mass, y = data$s1$intensity/max(data$s1$intensity),type="l",col="red")
  lines(x=data$s2$mass, y = data$s2$intensity/max(data$s2$intensity), col = "green")
  lines(x=data$s3$mass, y = data$s3$intensity/max(data$s3$intensity), col = "blue")
  
  bzzt <- deer_hits_chymo[[ii]]
  bzzt <- cbind(bzzt,pep_deer_chymo)
  bzzt <- bzzt[bzzt$hit,]
  message(sprintf("drawing %d hits",nrow(bzzt)))
  points(x=bzzt$mass1,y=0.5*bzzt$mass1/bzzt$mass1,pch=20,cex=1.5,col="orange")
  
  
}
dev.off()
```





#Appendix: Don't use bioconductor!

*I'm keeping this section in so that I remember not to try it again!*

We'll try reading Fasta files using bioconductor, although this may be a bit unweildy for our purposes. I'm following the example at [https://stackoverflow.com/questions/9328519/how-to-read-from-multiple-fasta-files-with-r]

let's install this (this may take some time, but you only need to do this once): 

```{r, eval=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite("ShortRead")

```


load the `bioconductor` library, and check the sequence:

```{r, eval=FALSE}
require("ShortRead",quietly = T)
fasta <- readFasta("../",".fasta")
fasta[1]@sread
```

Hmm.. that sequence seems to be picking a subset of the letters in the sequence in the file. Ah well, we'll have to roll our own reader - hopefully not too tricky




