
#Load sequences using `read.table`: 

```{r}
#fasta <- read.table("deer_collagen_20170915.fasta", stringsAsFactors = F)
fasta_mam <- load.mcs("sheep")

```

This gives us a simple table, the even rows of which are the sequences (in this particular application)


##setup the path for samples 
```{r}
file_path <- "C:/Users/GopaiahTalari/Desktop/25032018/Parchment_data/"
replicates <- c("_1","_2","_3")
```


##Loading red deer samples

The same process applies to deer - we just need to list the deer file bits like this:

```{r}
x <- list.files(file_path)
y <- as.data.frame(x) 
z <- rev(gregexpr("_", y$x)[[2]])[2]
y$name <- substr(y$x,1,(z+1))
sample_lots<- unique(y$name)
```

##making the list of samples

```{r warning=FALSE, include=FALSE}
sample_data<-list()
for(ii in 1:length(sample_lots)){
  froot <- sprintf("%s%s",file_path,sample_lots[ii])
  sample_data[[ii]] <- load.sample(froot=froot,name=sprintf("%s",sample_lots[ii]),replicates, fext = ".txt")

  }
```
# run mass_lag function (mass_lag)
# mass_lag function used for calculation of lag with the help of ms_align function from bacollite
# ts dataframe contains mass and lag values

```{r}
library(ggplot2)

#pdf(file="Robust_fit.pdf",w=12,h=8)
 
for(i in 1:1){
  sample_list <- sample_data[[i]]
  ts <- data.frame()
  ts <- mass_lag(fasta_mam,sample_data[[i]])
  names(ts)[1] <- c("pm1")
  #Sort the masss data by the order in pm1
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  nm <-sample_data[[i]][["name"]]
  masss_lagg <- myplot_robust(ts,nm,overlap = F)
  
}
#dev.off()
print(masss_lagg)

```

```{r}



write.csv(ts,"lags.csv")
```

```{r}
lag11<- ts[ts$lag1 < 0.5,]
boxplot(lag11)
```

```{r}
library(ggplot2)

for(i in 1: 1) {
  sample_list <- sample_data[[i]]
  ts <- data.frame()
  ts <- mass_lag(fasta_mam,sample_data[[i]])
  names(ts)[1] <- c("pm1")
  #Sort the masss data by the order in pm1
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  nm <-sample_data[[i]][["name"]]
  masss_lagg <- myplot1(ts,nm, overlap = F)
 
}
 print(masss_lagg)

```

# view the data structure of ts
```{r}
require(DT, quietly = T)
datatable(ts)
```

##making the ts datafrme contains column mass as pm1 and lags are lag1, lag2, lag3

```{r}
#change the name of mass column as pm1 in ts data frame
names(ts)[1] <- c("pm1")
#Sort the masss data by the order in pm1
ts <- ts[ order(ts$pm1), ]
ts <- ts[abs(ts$lag1) < 0.5,]
ts <- ts[abs(ts$lag2) < 0.5,]
ts <- ts[abs(ts$lag3) < 0.5,]
# view ts data frame
require(DT, quietly = T)
datatable(ts)
```
# run masss_lagg function
# masss_lagg function is used to gerate the plots for the lag vs mass 
# ggplot2 used to generate the 2 types of plots

```{r}
#required ggplot for ploting
library(ggplot2)

# To save the plot as png for high quality view
png("mas_lag.png", res = 600,width = 12,units = "in",height = 9)
masss_lagg <- myplot(ts,overlap = T)
print(masss_lagg)
dev.off()
print(masss_lagg)
```


```{r}
# To save the plot as png for high quality view

png("mas_lag2.png", res = 600,width = 12,units = "in",height = 9)
masss_lagg2 <- myplot(ts,overlap = F)
print(masss_lagg2)
dev.off()
print(masss_lagg2)
```



