---
title: "R Notebook"
output: html_notebook
---

#Load sequences using `read.table`: 

```{r}
#fasta <- read.table("deer_collagen_20170915.fasta", stringsAsFactors = F)
fasta_mam <- load.mcs()

```

This gives us a simple table, the even rows of which are the sequences (in this particular application)


##setup the path for samples 
```{r}
file_path <- "C:/Users/GopaiahTalari/Desktop/25032018/drive-download-20180511T164510Z-001/CSV_20141028_SF_BZ06-16_HH15-36/"
replicates <- c("_J12","_J15","_J18")
```


##Loading red deer samples

The same process applies to deer - we just need to list the deer file bits like this:



```{r}
sample_lots <- c("20141028_SF_BZ06_16_HH15_36")
```

##making the list of samples

```{r warning=FALSE, include=FALSE}
sample_data<-list()
for(ii in 1:length(sample_lots)){
  froot <- sprintf("%s%s",file_path,sample_lots[ii])
  sample_data[[ii]] <- load.sample(froot=froot,name=sprintf("%s",sample_lots[ii]),replicates, fext = ".txt")

  }
```

# run mass_lag function (mass_lag)
# mass_lag function used for calculation of lag with the help of ms_align function from bacollite
# ts dataframe contains mass and lag values
```{r}

```

```{r}
#library(ggplot2)

#pdf(file="Robust_fit.pdf",w=12,h=8)
ts <- data.frame() 
for(i in 1:length(sample_data)){
  ts <- mass_lag(fasta_mam,sample_data[[i]])
  names(ts)[1] <- c("pm1")
  #Sort the masss data by the order in pm1
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  #nm <-sample_data[[i]][["name"]]
  #df1 <- reshape2::melt(ts, id = "pm1")
  mas_lag_before <- myplot_lm(ts,nm,overlap = F)
}
#dev.off()
#print(masss_lagg)
```




```{r}
#df1 <- reshape2::melt(ts, id = "pm1")

  
#model1 <- lm(df1$value[df1$variable=="lag1"] ~ poly(df1$pm1[df1$variable=="lag1"],3))

R_sqare <- readline(prompt= "Enter required_R_sqare: ")
# convert character into integer
R2 <- as.numeric(R_sqare)


ts1 <- ts
st <- list()
#a <-0
for (i in 1:length(ts1$pm1)){
#i<-1
  
  model1 <- lm(ts1$lag1 ~ poly(ts1$pm1,3))
  model2 <- lm(ts1$lag2 ~ poly(ts1$pm1,3))
  model3 <- lm(ts1$lag3 ~ poly(ts1$pm1,3))

  #err1 <- summary(model1)$sigma
  ts1$list_residual1 <- resid(model1)
  ts1$list_residual2 <- resid(model2)
  ts1$list_residual3 <- resid(model3)
  #list_residual<- data.frame(list_residual1, "pm1"=ts1$pm1)
  #ts1 <- cbind(ts1,list_residual)
  #ts1$pm1<-NULL
  ts1<- ts1[-which.max(ts1$list_residual1),]
  ts1<- ts1[-which.min(ts1$list_residual1),]
  
  ts1<- ts1[-which.max(ts1$list_residual2),]
  ts1<- ts1[-which.min(ts1$list_residual2),]
  
  ts1<- ts1[-which.max(ts1$list_residual3),]
  ts1<- ts1[-which.min(ts1$list_residual3),]
  
  
  st1 <- summary(model1)$r.squared
  st <- append(st,st1)
  
  #i<-14
  #a<-13
if (st[[i]] > R2 ){
    break
#}else{
    print(st)
  }
 #a = 1
}
data_for_plot<- ts1[,c(1:4)]
mas_lag_after <- myplot_lm(data_for_plot,nm,overlap = F)
mas_lag_after 
```

# view the data structure of ts
```{r}
png("before_vs_after_outliers.png",res = 600,width = 12,units = "in",height = 10 )
gridExtra::grid.arrange(mas_lag_before,mas_lag_after, nrow=2, top = "Before and after removing outliers")
#ggsave("before_vs_after_outliers.png",res = 600,width = 12,units = "in",height = 9)
dev.off()
print(before_after)
```

##making the ts datafrme contains column mass as pm1 and lags are lag1, lag2, lag3

```{r}
#change the name of mass column as pm1 in ts data frame
names(ts)[1] <- c("pm1")
#Sort the masss data by the order in pm1
ts <- ts[ order(ts$pm1), ]
ts <- ts[abs(ts$lag1) < 0.5,]
ts <- ts[abs(ts$lag2) < 0.5,]
ts <- ts[abs(ts$lag3) < 0.5,]
# view ts data frame
require(DT, quietly = T)
datatable(ts)
```
# run masss_lagg function
# masss_lagg function is used to gerate the plots for the lag vs mass 
# ggplot2 used to generate the 2 types of plots

```{r}
#required ggplot for ploting
library(ggplot2)

# To save the plot as png for high quality view
png("mas_lag.png", res = 600,width = 12,units = "in",height = 9)
masss_lagg <- myplot(ts,overlap = T)
print(masss_lagg)
dev.off()
print(masss_lagg)
```


```{r}
# To save the plot as png for high quality view

png("mas_lag2.png", res = 600,width = 12,units = "in",height = 9)
masss_lagg2 <- myplot(ts,overlap = F)
print(masss_lagg2)
dev.off()
print(masss_lagg2)
```



