---
title: "R Notebook"
output: html_notebook
---

#Load sequences using `read.table`: 

```{r}

library(openxlsx)

Data1_fasta_human<- load.human.markers()

#write.csv(fasta_human, "list_of_Human_peptides.csv", quote = F)

marker_sheep <- load.mcs("sheep")
marker_sheep_in_hum1 <- fasta_human[fasta_human$seq %in% marker_sheep$seq,]
marker_sheep_in_hum <- marker_sheep_in_hum1[,c(2,10)]
#write.csv(file="sheep_markers_in_human.csv",shm,quote=F)

sheep_marker_SF <- read.xlsx("sheep_markers_SF.xlsx")

Both_sheep_markers <- rbind.data.frame(marker_sheep_in_hum ,sheep_marker_SF)
Data2_Both_sheep_markers <- Both_sheep_markers[order(Both_sheep_markers$mass1),]


```

This gives us a simple table, the even rows of which are the sequences (in this particular application)


##setup the path for samples 

```{r}
#sample_files_path

file_path<- "C:/Users/GopaiahTalari/Desktop/25032018/drive-download-20180511T164510Z-001/CSV_20141028_SF_BZ06-16_HH15-36/"
file_path2 <- "C:/Users/GopaiahTalari/Desktop/25032018/drive-download-20180511T164510Z-001/CSV_20141126_SF_BZ17-45_BZ89_IMI01-12rep/"
file_path3 <- "C:/Users/GopaiahTalari/Desktop/25032018/drive-download-20180511T164510Z-001/CSV_20141127_SF_BZ46-77_RESPOT/"
file_path4 <- "C:/Users/GopaiahTalari/Desktop/25032018/drive-download-20180511T164510Z-001/CSV_20141128_SF_BZ82-88_BBZ01-09_UMLB01-12/"


```



```{r}
#making the list of the samples from the folder

x <- list.files(file_path,pattern = ".txt")

sd <- ifelse(grepl("BZ",x), paste(x), NA) 
sd1 <- sd[!is.na(sd)]

y <- as.data.frame(sd1)

#y$name <- ifelse(rev(gregexpr("_", i)[[1]])[1],)
df2 <- data.frame()
for (i in sd1) {
  
  z1 <- rev(gregexpr("_", i)[[1]])[1]
  name<- substr(i, 1, (z1))
  num <-  substr(i, z1+1, (z1+3))
  df3 <- data.frame(name,num)
  df2 <- rbind(df2,df3)
}

sample_list <- df2$name
```


##making the list of samples

```{r warning=FALSE, include=FALSE}
library(openxlsx)

path <- paste(file_path,"PLATEMAP.xlsx", sep = "")
df <- read.xlsx(path,skipEmptyRows = T, colNames = FALSE)
df1<- df[grepl("BZ", df$X5),]


numb<- c()
a <- 1
for (i in 1:(length(df1$X5)/3)) {
  numb <-append(numb,a)
  a<- a+3
}
# aa <- c()
  
```

#replicates_labelling
```{r}
replicates<- list()
for(i in numb){
  # print(i)
  p <- df1$X4[i:(i+2)]
  print(p)
  replicates[[i]]<- p
  
  non_null_names <- which(!sapply(replicates, is.null))
  replicates <- replicates[non_null_names]
}

```

#sample list
```{r}
samples1_list<-list()

for(ii in 1:length(replicates)){
  #message(sprintf("Opening %s%s%s.txt",file_path,elk_lots[ii],replicates[1]))
  froot <- sprintf("%s%s",file_path,sample_list[ii])
  samples1_list[[ii]] <-load.sample(froot=froot,name=sprintf("%s",sample_list[ii]),replicates[[ii]], fext = ".txt")
  
}

```

# run mass_lag function (mass_lag)
# mass_lag function used for calculation of lag with the help of ms_align function from      bacollite
# ts dataframe contains mass and lag values
# Generating the pdf file with R2 score
```{r}
library(ggplot2)

pdf(file="C:/Users/GopaiahTalari/Desktop/25032018/Try_with_guass/Before_outlier_fit_human_with_guass.pdf",w=12,h=8)
 
for(i in 1:length(samples1_list)){
  ts <- data.frame()
  ts <- mass_guass_lag(Data1_fasta_human,samples1_list[[i]])
  names(ts)[1] <- c("pm1")
  #Sort the masss data by the order in pm1
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  nm1 <- samples1_list[[i]][["name"]]
  nm2 <-samples1_list[[i]][["spot"]]
  nm <- paste(nm1,nm2,sep = "")
  mas_lag_before <- myplot_lm(ts,nm,overlap = F)
  print(mas_lag_before)
}
dev.off() 

```


```{r}
library(ggplot2)

pdf(file="C:/Users/GopaiahTalari/Desktop/25032018/Try_with_guass/Before_outlier_fit_human_without_guass.pdf",w=12,h=8)
 
for(i in 1:length(samples1_list)){
  ts <- data.frame()
  ts <- mass_lag(Data1_fasta_human,samples1_list[[i]])
  names(ts)[1] <- c("pm1")
  #Sort the masss data by the order in pm1
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  nm1 <- samples1_list[[i]][["name"]]
  nm2 <-samples1_list[[i]][["spot"]]
  nm <- paste(nm1,nm2,sep = "")
  mas_lag_before <- myplot_lm(ts,nm,overlap = F)
  print(mas_lag_before)
}
dev.off() 
```





```{r}

library(ggplot2)

pdf(file="C:/Users/GopaiahTalari/Desktop/25032018/Try_with_guass/Before_outlier_fit_Sarah_F_sheep_without_guass.pdf",w=12,h=8)
 
for(i in 1:length(samples1_list)){
  ts <- data.frame()
  ts <- mass_lag_seq(sheep_marker_SF,samples1_list[[i]])
  names(ts)[1] <- c("pm1")
  #Sort the masss data by the order in pm1
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  nm1 <- samples1_list[[i]][["name"]]
  nm2 <-samples1_list[[i]][["spot"]]
  nm <- paste(nm1,nm2,sep = "")
  mas_lag_before <- myplot_lm(ts,nm,overlap = F)
  print(mas_lag_before)
}
dev.off()

```

```{r}
library(ggplot2)

pdf(file="C:/Users/GopaiahTalari/Desktop/25032018/Try_with_guass/Before_outlier_fit_sheep_with_guass.pdf",w=12,h=8)
 
for(i in 1:length(samples1_list)){
  ts <- data.frame()
  ts <- mass_lag_guass_seq(Data2_Both_sheep_markers,samples1_list[[i]])
  names(ts)[1] <- c("pm1")
  #Sort the masss data by the order in pm1
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  nm1 <- samples1_list[[i]][["name"]]
  nm2 <-samples1_list[[i]][["spot"]]
  nm <- paste(nm1,nm2,sep = "")
  mas_lag_before <- myplot_lm(ts,nm,overlap = F)
  print(mas_lag_before)
}
```

```{r}
library(ggplot2)

pdf(file="C:/Users/GopaiahTalari/Desktop/25032018/Try_with_guass/Both_human_sheep_guass.pdf",w=12,h=8)
 
for(i in 1:length(samples1_list)){
  ts <- data.frame()
  ts <- mass_lag_guass_seq(Data2_Both_sheep_markers,samples1_list[[i]])
  names(ts)[1] <- c("pm1")
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  
  ts$id <- paste("SH")
  
  ts1 <- data.frame()
  ts1 <- mass_guass_lag(Data1_fasta_human,samples1_list[[i]])
  names(ts1)[1] <- c("pm1")
  ts1 <- ts1[ order(ts1$pm1), ]
  ts1 <- ts1[abs(ts1$lag1) < 0.5,]
  ts1 <- ts1[abs(ts1$lag2) < 0.5,]
  ts1 <- ts1[abs(ts1$lag3) < 0.5,]
  nm1 <- samples1_list[[i]][["name"]]
  nm2 <-samples1_list[[i]][["spot"]]
  nm <- paste(nm1,nm2,sep = "")
  ts1$id <- paste("HM")
  
  ts_both <- rbind.data.frame(ts,ts1)
  mas_lag_before <- myplot_two(ts_both,nm,overlap = F)
  print(mas_lag_before)
  
  #df1 <- reshape2::melt(ts_both, id.vars = c("pm1", "id"))
}
dev.off()

```

```{r}
library(ggplot2)
R2 <- 0.20

pdf(file="After_Both_human_sheep.pdf",w=12,h=8)
 #
for(i in 1){
  ts <- data.frame()
  ts <- mass_lag_seq(Data1_fasta_human,samples1_list[[i]])
  names(ts)[1] <- c("pm1")
  ts <- ts[ order(ts$pm1), ]
  ts <- ts[abs(ts$lag1) < 0.5,]
  ts <- ts[abs(ts$lag2) < 0.5,]
  ts <- ts[abs(ts$lag3) < 0.5,]
  ts1 <- ts
  st <- list()
  #a <-0
  for (i in 1:length(ts1$pm1)){
  #i<-1
  
  model1 <- lm(ts1$lag1 ~ poly(ts1$pm1,3))
  model2 <- lm(ts1$lag2 ~ poly(ts1$pm1,3))
  model3 <- lm(ts1$lag3 ~ poly(ts1$pm1,3))

  #err1 <- summary(model1)$sigma
  ts1$list_residual1 <- resid(model1)
  ts1$list_residual2 <- resid(model2)
  ts1$list_residual3 <- resid(model3)
  #list_residual<- data.frame(list_residual1, "pm1"=ts1$pm1)
  #ts1 <- cbind(ts1,list_residual)
  #ts1$pm1<-NULL
  ts1<- ts1[-which.max(ts1$list_residual1),]
  ts1<- ts1[-which.min(ts1$list_residual1),]
  
  ts1<- ts1[-which.max(ts1$list_residual2),]
  ts1<- ts1[-which.min(ts1$list_residual2),]
  
  ts1<- ts1[-which.max(ts1$list_residual3),]
  ts1<- ts1[-which.min(ts1$list_residual3),]
  
  
  st1 <- summary(model1)$r.squared
  st <- append(st,st1)
  
  #i<-14
  #a<-13
  if (st[[i]] > R2 ){
     break 
  }#else{
    #print(st)
  #}
  #a = 1
  }
  
  #data_for_plot$id <- paste("SH")
  # ####################################################################marker2
  # ts2 <- data.frame()
  # ts2 <- mass_lag(Data1_fasta_human,samples1_list[[i]])
  # names(ts2)[1] <- c("pm1")
  # ts2 <- ts2[ order(ts2$pm1), ]
  # ts2 <- ts2[abs(ts2$lag1) < 0.5,]
  # ts2 <- ts2[abs(ts2$lag2) < 0.5,]
  # ts2 <- ts2[abs(ts2$lag3) < 0.5,]
  # ts1 <- ts2
  # st <- list()
  # #a <-0
  # for (i in 1:length(ts1$pm1)){
  # #i<-1
  # 
  # model1 <- lm(ts1$lag1 ~ poly(ts1$pm1,3))
  # model2 <- lm(ts1$lag2 ~ poly(ts1$pm1,3))
  # model3 <- lm(ts1$lag3 ~ poly(ts1$pm1,3))
  # 
  # #err1 <- summary(model1)$sigma
  # ts1$list_residual1 <- resid(model1)
  # ts1$list_residual2 <- resid(model2)
  # ts1$list_residual3 <- resid(model3)
  # #list_residual<- data.frame(list_residual1, "pm1"=ts1$pm1)
  # #ts1 <- cbind(ts1,list_residual)
  # #ts1$pm1<-NULL
  # ts1<- ts1[-which.max(ts1$list_residual1),]
  # ts1<- ts1[-which.min(ts1$list_residual1),]
  # 
  # ts1<- ts1[-which.max(ts1$list_residual2),]
  # ts1<- ts1[-which.min(ts1$list_residual2),]
  # 
  # ts1<- ts1[-which.max(ts1$list_residual3),]
  # ts1<- ts1[-which.min(ts1$list_residual3),]
  # 
  # 
  # st1 <- summary(model1)$r.squared
  # st <- append(st,st1)
  # 
  # #i<-14
  # #a<-13
  # if (st[[i]] > R2 ){
  #    break 
  # }
  # 
  # }
  # data_for_plot2<- ts1[,c(1:4)]
  # 
  # data_for_plot2$id <- paste("HM")
  # #ts2$id <- paste("HM")
  # 
  # ts_both <- rbind.data.frame(data_for_plot,data_for_plot2)
  # mas_lag_before <- myplot_two(ts_both,nm,overlap = F)
  # print(mas_lag_before)
  # 
  # #df1 <- reshape2::melt(ts_both, id.vars = c("pm1", "id"))
}
dev.off()
data_for_plot <- ts1[,c(1:4)]

```



```{r}
#df1 <- reshape2::melt(ts, id = "pm1")

  
#model1 <- lm(df1$value[df1$variable=="lag1"] ~ poly(df1$pm1[df1$variable=="lag1"],3))

R_sqare <- readline(prompt= "Enter required_R_sqare: ")
# convert character into integer
R2 <- as.numeric(R_sqare)
R2 <- 0.20

ts1 <- ts
st <- list()
#a <-0
for (i in 1:length(ts1$pm1)){
#i<-1
  
  model1 <- lm(ts1$lag1 ~ poly(ts1$pm1,3))
  model2 <- lm(ts1$lag2 ~ poly(ts1$pm1,3))
  model3 <- lm(ts1$lag3 ~ poly(ts1$pm1,3))

  #err1 <- summary(model1)$sigma
  ts1$list_residual1 <- resid(model1)
  ts1$list_residual2 <- resid(model2)
  ts1$list_residual3 <- resid(model3)
  #list_residual<- data.frame(list_residual1, "pm1"=ts1$pm1)
  #ts1 <- cbind(ts1,list_residual)
  #ts1$pm1<-NULL
  ts1<- ts1[-which.max(ts1$list_residual1),]
  ts1<- ts1[-which.min(ts1$list_residual1),]
  
  ts1<- ts1[-which.max(ts1$list_residual2),]
  ts1<- ts1[-which.min(ts1$list_residual2),]
  
  ts1<- ts1[-which.max(ts1$list_residual3),]
  ts1<- ts1[-which.min(ts1$list_residual3),]
  
  
  st1 <- summary(model1)$r.squared
  st <- append(st,st1)
  
  #i<-14
  #a<-13
if (st[[i]] > R2 ){
   break
#}else{
    print(st)
  }
 #a = 1
    # if (i== 2){
    #   break
    # }
}
data_for_plot<- ts1[,c(1:4)]
mas_lag_after <- myplot_lm(data_for_plot,nm,overlap = F)
print( )
```

# view the data structure of ts

```{r}
png("before_vs_after_outliers.png",res = 600,width = 12,units = "in",height = 10 )
gridExtra::grid.arrange(mas_lag_before,mas_lag_after, nrow=2, top = "Before and after removing outliers")
#ggsave("before_vs_after_outliers.png",res = 600,width = 12,units = "in",height = 9)
#dev.off()
#print(before_after)
```



```{r}
fit_x<- ts1[,c(1)]
write.csv(fit_x, "list_of_best_fit_peptides.csv")


```



```{r}
#change the name of mass column as pm1 in ts data frame
names(ts)[1] <- c("pm1")
#Sort the masss data by the order in pm1
ts <- ts[ order(ts$pm1), ]
t
s <- ts[abs(ts$lag1) < 0.5,]
ts <- ts[abs(ts$lag2) < 0.5,]
ts <- ts[abs(ts$lag3) < 0.5,]
# view ts data frame
require(DT, quietly = T)
datatable(ts)
```

# run masss_lagg function
# masss_lagg function is used to gerate the plots for the lag vs mass 
# ggplot2 used to generate the 2 types of plots


```{r}
#required ggplot for ploting
library(ggplot2)

# To save the plot as png for high quality view
png("mas_lag.png", res = 600,width = 12,units = "in",height = 9)
masss_lagg <- myplot(ts,overlap = T)
print(masss_lagg)
dev.off()

print(masss_lagg)

```



```{r}
# To save the plot as png for high quality view

png("mas_lag2.png", res = 600,width = 12,units = "in",height = 9)
masss_lagg2 <- myplot(ts,overlap = F)
print(masss_lagg2)
dev.off()

print(masss_lagg2)

```



