---
title: "Present Results"
output:
  html_notebook: default
  html_document: default
---

```{r}
#Setting up the job:
#- load the `stringr` package for string manipulation
require(stringr)
```


Here we go through the files and structures used in `Process.Rmd` and print the matches. This saves having to re-calculate them as it takes about 4 hours!

Some observations:
- the 'score' is the proportion of the ions explained by the peaks. This is generally a low number because we are only looking at 12 peaks out of the whole
spectrum
- generally, the higher the score, the more consistent the match across replicates
- scores below ~0.01 should probably be considered to be noise
- where scores are identical across many species, we are only getting good alignments for a subset of the peptides
- There's lots of scope for increasing the efficiency of the code - I wanted to focus on getting reasonable results at this point. 

- it would be reasonable to combine the replicate scores to come up with a 'final' classification for each sample. I've not done that here because I think it's useful
to see how each individual spectrum is being classified at this point. 


```{r}
rr = 0
rk <- c(1:10)
for(ff in seq(1,length(samples),3)){
  ii = ff + (rr %% 3)
  if(ii< length(samples) && is.na(str_match(samples[ii],"Reference")) && ii != 251){
    message(sprintf(" %s%s%s",
                    str_pad(samples[ii+0],34),
                    str_pad(samples[ii+1],33),
                    str_pad(samples[ii+2],33)
                    ))
    message("------------------------------------------------------------------------------------------------------")
    
    message(sprintf("%02d %s %0.5f%s %0.5f%s %0.5f\n", rk,
                      str_pad(cl[[ii+0]]$species[ranks],25),cl[[ii+0]]$ions[ranks],
                      str_pad(cl[[ii+1]]$species[ranks],25),cl[[ii+1]]$ions[ranks],
                      str_pad(cl[[ii+2]]$species[ranks],25),cl[[ii+2]]$ions[ranks]

                    
                    ))
    
    message("")
    
    
    
    
  }
  #increment rr when we hit the reference samples
  if(ff == 139) rr = rr+ 1
  
}

```
